%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% CV Nilang Nandan 06/2019 %%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\PassOptionsToPackage{dvipsnames}{xcolor}
\documentclass[10pt,a4paper]{altacv}

%Layout
\geometry{left=1cm,right=9cm,marginparwidth=6.8cm,marginparsep=1.2cm,top=1.25cm,bottom=1.25cm,footskip=2\baselineskip}

%Packages
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[default]{lato}
\usepackage{hyperref}

%Colors

\definecolor{accent}{HTML}{000e17}
\definecolor{heading}{HTML}{000e17}
\definecolor{emphasis}{HTML}{696969}
\definecolor{body}{HTML}{01415f}

\colorlet{heading}{heading}
\colorlet{accent}{accent}
\colorlet{emphasis}{emphasis}
\colorlet{body}{body}

\renewcommand{\itemmarker}{{\small\textbullet}}
\renewcommand{\ratingmarker}{\faCircle}

%

\begin{document}
\name{NILANG NANDAN}
\tagline{IIT Guwahati Graduate \& Technology enthusiast}
% \photo{2.5cm}{BrunoAlves}
\personalinfo{
    \printinfo{\faBirthdayCake}{14th Jan 1996}
    \email{nilangnandan@gmail.com}
    \phone{+91 9065280428}
%    \mailaddress{SR Njemačke 6, 10000}
    \location{Hyderabad, India}
    \linkedin{linkedin.com/in/nilang-nandan}
%    \homepage{jaksatomovic.github.io}
%    \github{github.com/jaksatomovic}
}

%

\begin{fullwidth}
\makecvheader
\end{fullwidth}

%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Experience %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\cvsection[page1sidebar]{Experience}

%%%%%%%%%%%%%
%Experience 1
%%%%%%%%%%%%%

\cvevent{Associate Consultant - Technology}{Virtusa Consulting Services}{Jan 2020 -- Ongoing}{Hyderabad, India}

\begin{itemize}
    \setlength{\itemindent}{0.5em}
    \item[--]   \small{Working in xLabs, R\&D division of Virtusa}
    % \item[--]   \small{Working in xLabs, R\&D division of Virtusa}
    \item[--]   \small{Developing software using \textbf {Python}}
    \item[--]   \small{Version Control using Git}
\end{itemize}

\medskip

%%%%%%%%%%%%%
%Experience 2
%%%%%%%%%%%%%

\cvevent{Engineer}{Virtusa Consulting Services}{June 2018 -- Jan 2020}{Hyderabad, India}

%\begin{itemize}
%    \item Fullstack JAVA developer
%\end{itemize}

% \begin{itemize}
%     \setlength{\itemindent}{0.5em}
% \end{itemize}

\medskip

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Projects %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\cvsection[page2sidebar]{Projects}

%%%%%%%%%%%%%
%Project 1
%%%%%%%%%%%%%

\cvproject{Synthetic Data Generator}
\begin{itemize}
  \item \small {\textbf {Python} based tool which can generate data from configurable file.}
  \item \small {Generate time-series data with the control over their frequency and period of occurrence.}
  \item \small {Multiple generator to generate data based on different rules/conditions.}
  \item \small {Techs: \textbf {Python 3}, \textbf {Flask}, SQLAlchemy, Mimesis API,  Pandas, Numpy}
\end{itemize}

% \divider

%

%%%%%%%%%%%%%
%Project 2
%%%%%%%%%%%%%

\cvproject{Data Anonymization}

\begin{itemize}
  \item \small {\textbf {Python} based tool for information sanitization such that person whom the data describe remains anonymous.}
  \item \small {Based on defined configuration for column, apply different techniques to anonymise.}
  \item \small {Anonymization techniques: Pseudonymization, Differential Privacy, Masking, Noise Addition, Swapping, Aggregation, Generalization, Perturbation, Synthetic Data.}
  \item \small {Testing methods: k-anonymity, l-diversity, t-closeness, wasserstein distance.}
%   \item \small {Techs: \textbf {Python 3}, \textbf {Flask}, SQLAlchemy, Mimesis API,  Pandas, Numpy}
\end{itemize}

%

%%%%%%%%%%%%%
%Project 3
%%%%%%%%%%%%%

\cvproject{Data Lake for AI/ML}

\begin{itemize}
  \item \small {Designed and setup data lake for AI/ML project on Google Cloud Platform (GCP).}
  \item \small {Supported input method: Stream and Batch mode.}
  \item \small {Component used: Cloud Storage, Cloud Datalab, Cloud Dataflow, Cloud PUB/SUB, Cloud BigTable, BigQuery}
\end{itemize}

%%%%%%%%%%%%%
%Project 4
%%%%%%%%%%%%%

\cvproject{Swagger CodeGen}

\begin{itemize}
  \item \small {Code-gen-tool is a java library/component designed to generate sample microservice code based on the input information provided by developer/user.}
  \item \small {This tool can also be extended for cresting any additional generic files or any generic configurations which are required in microservice code.}
\end{itemize}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Certificates %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\cvsection{POSITION OF RESPONSIBILITY}

%%%%%%%%%%%%%
%Certificate 1
%%%%%%%%%%%%%

\cvproject{Chief Organizer | Guwahati Half Marathon 2016}
\begin{itemize}
  \item \small {The largest Marathon of Northeast India to be completely organized by the student fraternity with the theme \textbf {Run for Tobacco free India}.}
\end{itemize}
\divider

%%%%%%%%%%%%%
%Certificate 2
%%%%%%%%%%%%%

\cvproject{Chief Organizer | Wake Up And Vote 2016}
\begin{itemize}
  \item \small {A social campaign by Techniche, IIT Guwahati to raise awareness and importance of voting among people before legislative election of Assam in 2016.}
\end{itemize}
\divider

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Interests %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% \cvsection{Interests}

% \wheelchart{1.5cm}{0.5cm}{%
%   10/10em/accent!30/Electronics,
%   25/9em/accent!60/Science,
%   5/13em/accent!10/Movies,
%   20/15em/accent!40/Sport,
%   30/9em/accent/Technology,
%   5/8em/accent!20/Literature
% }


%%New Page
% \clearpage




\end{document}
